---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zeyushiny

<!-- badges: start -->
<!-- badges: end -->

The goal of `zeyushiny` is to embed my shiny application and make it lunch via `launch_app()` function exported by my package.

## Installation

You can install the development version from [GitHub](https://github.com/etc5523-2020/r-package-assessment-zyliu178.git) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-zyliu178")
```

# Data Description

The first data used in this blog was obtained from: the Center for Systems Science and Engineering (CSSE), which is a research collective housed within the Department of Civil and Systems Engineering (CaSE) at Johns Hopkins University (JHU). The second data used in this blog was obtained from the World Health Organization, which is an international organization to create a better and healthier future for people all over the world.

## Example

Trend of total confirmed cases in China

``` r
library(zeyushiny)
# Load shiny application
launch_app()
```

```{r, message = FALSE}
library(tidyverse)
library(zeyushiny)
cov_total %>% filter(month <=2) %>%
  ggplot(aes(x = Date_reported, y = Cumulative_cases)) + 
            geom_point() +
            geom_smooth(se = FALSE) +
            theme(legend.title = element_blank()) +
            xlab("Date") +
            theme_light() +
            ylab("Total confirmed cases") +
            theme(legend.position = "none") +
            ggtitle("Trend of total confirmed cases in China")
```